Defending Byzantine Attacks in Ensemble Federated Learning: A Reputation-based Phishing Approach

### 2022-03-01 Manuscript_TIFS/manuscript_TIFS.tex
framework图片修改和实验设置表

  \renewcommand\arraystretch{1.5}
  \centering
  \caption{Parameter Settings}
  \resizebox{0.5\textwidth}{!}{
  \label{tab:my-table}
  \begin{tabular}{l|l}
    \bottomrule
    \textbf{Parameter}                    & \textbf{Parameter Value}              \\ \hline
    Number of clients                         & 50 clients                                \\ \hline
    Number of samples                  & 60000 samples                             \\ \hline
    \multirow{2}{*}{Number of samples in each client} & 800 training samples                      \\
                                          & 200 test samples                          \\ \hline
    \multirow{2}{*}{Number of samples in the server} & 8000 unlabeled samples                    \\
                                          & 2000 labeled samples                      \\ \hline
    Number of iterations                       & 10 iterations                                 \\ \hline
    \multirow{2}{*}{Number of samples in each iteration}  & 800 unlabeled samples                     \\
                                          & 200 labeled samples                       \\ \hline
    Deep learning model                   & Residual Networks                         \\ \hline
    Byzantine fractions $p$               & 0,0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9     \\ \hline
    Imbalance degrees $q$                  & 0.1,0.2,0.5,0.6,0.7,0.8               \\ \hline
    Datasets $d$                         & MNIST,Fashion-MNIST,CIFAR-10              \\ \hline
    \end{tabular}
}
\end{table}

>>>>

  \renewcommand\arraystretch{1.5}
  \centering
  \caption{Parameter Settings}
  \resizebox{0.5\textwidth}{!}{
  \label{tab:my-table}
  \begin{tabular}{l|l}
    \bottomrule
    \textbf{Parameter}                    & \textbf{Parameter Value}              \\ \hline
    No. clients                         & 50 clients                                \\ \hline
    No. samples                  & 60000 samples                             \\ \hline
    \multirow{2}{*}{No. samples in each client} & 800 training samples                      \\
                                          & 200 test samples                          \\ \hline
    \multirow{2}{*}{No. samples in the server} & 8000 unlabeled samples                    \\
                                          & 2000 labeled samples                      \\ \hline
                                          No. iterations                       & 10 iterations                                 \\ \hline
    \multirow{2}{*}{No. samples in each iteration}  & 800 unlabeled samples                     \\
                                          & 200 labeled samples                       \\ \hline
    Deep learning model                   & Residual Networks                         \\ \hline
    Byzantine fractions $p$               & 0,0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9     \\ \hline
    Imbalance degrees $q$                  & 0.1,0.2,0.5,0.6,0.7,0.8               \\ \hline
    Datasets $d$                         & MNIST,Fashion-MNIST,CIFAR-10              \\ \hline
    \end{tabular}
}
\end{table}
